\chapter[Characterization]{Characterization of Pulsars and Sub-Luminous Populations}
\label{chapter:collaborationWork}

This chapter focuses on work done in collaborations with others.
Main contributions are in modeling polarization position angle data
using the rotating vector model (RVM) and the numerical model. 
Example work will include use
of the models 
for general characterization of pulsars
and for a population study of $\gamma$-ray sub-luminous pulsars.
Because of the collaborative nature of the
work, this chapter will also focus on the broader use of polarization
data in conjunction with other types of data.
For the most part, $\gamma$-ray
modeling was performed by Roger W. Romani.

First, We will discuss the paper ``PSRs J$0248+6021$ and J$2240+5832$: Young Pulsars 
in the Northern Galactic Plane. Discovery, Timing, and Gamma-ray observations''
\citep{theureau2011psrs} in which two pulsars are reported as detected in the $\gamma$-ray
by the {\it Fermi} Large Area Telescope.  Many properties of the pulsars are characterized
using $\gamma$-ray and radio data.

PSR J1119-6127 is likewise characterized in ``Observations of Energetic High Magnetic Field Pulsars with the
{\it Fermi} Large Area Telescope'' \citep{parent2011observations}.  
A number of high magnetic field pulsars are discussed in the paper and PSR J1119-6127
is analyzed with a single-altitude polarization model.

In ``Broad-Band KeV to MeV Characteristics Of Soft Gamma-Ray Pulsar PSR J1513$-$5908''
\citep{hartogJ1513}, the pulsar PSR J1513$-$5908 (B1509$-$58) is analyzed in a 
number of wavelengths using revisited and updated data.  We analyze the
radio polarization using a single-altitude model.

The pulsar PSR J0737$-$3039A is analyzed using a two-altitude 
polarization model in ``{\it Fermi} LAT Pulsed
Detection of PSR J0737$-$3039A in the Double Pulsar System''.
We also include scattering effects in this model although it 
is difficult to reproduce the scattering effects seen in the data.  
This pulsar has complex polarization, which we selectively
cut.  This pulsar is particularly interesting because few
mildly spun-up pulsars have been detected in the $\gamma$-rays.

Finally, We will discuss the paper ``Sub-luminous $\gamma$-Ray Pulsars''
\citep{romani2011sub}.  The paper examines a number of young radio pulsars
that are weak in the $\gamma$-rays.  We try to determine
whether this sub-luminosity is due to
aligned geometry
using geometric constraints 
(including six pulsars for which we perform analysis using radio polarization).


\input{chapters/multiWaveLength/sections/characterizationOfJ0248+6021andJ2240+5832.tex}
\input{chapters/multiWaveLength/sections/highMagneticFeildPulsars}
\input{chapters/multiWaveLength/sections/characteristicsOfJ1513-5908}
\input{chapters/multiWaveLength/sections/characteristicsOfJ0737-3039A}
\input{chapters/multiWaveLength/sections/subLuminous.tex}

\section{Conclusions}

In this chapter, several papers are reviewed which take advantage of the 
polarization data to better understand the nature of pulsars.
From the work in these papers, we can see the important role of 
the polarization modeling for radio position angle measurements. 
Both numerical models and RVM were utilized in these studies.
Often times, the rotating vector model is a helpful and easy-to-used model to
interpret
polarization when applied to suitable data.
Additionally, we see the importance of using polarization data in
connection to other wavelengths.
