\prefacesection{Acknowledgement}

This thesis and indeed this degree 
is an accumulation of a lifetime 
of work.  Physics has been my passion and love for
many, many years but I could not have done any of this without
the wonderful support of my network of mentors, peers, and family.

First, I would like to thank my undergraduate research mentors
Richard Hennig, Richard Scalettar, Tristan Ursell, Linton Corruccini,
and Rob Phillips.
I truly would never have gone this far without your encouragement.

I would like to acknowledge my community college teachers 
Gary Emmery, Irene McGary, William Simpson, Kathy Monaghan, Forrest Newman,
Timothy Wei, Charlie Bennett, Jim Collins, Michael Maddox, Binh Truong, and Thomas Logan.
You gave me the foundations of my education.

I recognize my many friends and homework buddies from undergraduate at the University of California, Davis:
Nasim Eibagi, Hilary Brunner, Ingrid Neumann, 
Alex Spears, Jerome Latona, Matt Klint, Aru Rattanachata,
Christopher Varney, Lucy Zuniga, Amara Miller, Mark Triplett,
Colin McEnroe, Jim Lin, and Max Shchemelinin.
I enjoyed working and studying with all of you.

My professors from the University of California, Davis solidified my 
understanding of physics and gave me the courage and confidence I needed for 
graduate school.  I thank Manuel Calderon de la Barca Sanchez, Nicholas Curro, Rena Zieve,
Daniel Cebra, David Webb, John Rundle, Warren Pickett, Nicholas Curro, and Daniel Ferenc. 

I thank my many peers, colleagues, classmates, and roommates who have made my experience 
at Stanford rich. I acknowledge
Victoria Martin, Ruby Lai, Jaehwan Kang, Richard Anantua,
Adam Wright, Ondrej Urban, Terry Reyes, Rachel Meyer, Yuanyuan Su,
Meredith Trotter, Caitlin O'Brien, Steven Ehlert, Rebecca Hernandez, Renee Lizcano-Roales, Kruttika Vijay,
Ted Sanders, Patrick Kelly, Ariel Mendez, Mollie Jacobs, Kara Scheu, Sofia Izmailov, Karen Tkach, Stacy Lewis,
Matt Stadnik, Sasha Brownsberger, Kiel Howe,
Rebecca Nie, Phil Marshall, Masha Baryakhtar, Yao-Yuan Mao, Jane Dai,
Paul Simeon, Yvonne Kung, Alice Allafort, Jonathan Maltz,
Andrew Keller, Nicole Ackerman, Eric Spanton, Ning Bao,  
Matt Noll, Ryan Hamerly, Yu He, Tony Li, Eric Eason,
Georges Ndabashimiye, Mandeep Gill, JJ Lee, Kunal Sahasrabuddhe,
Sho Uemura, Tim Kovachy, Menyoung Lee, Gabe Billings, Alex Countryman, Kristi Schneck,
Kimmy Wu, Rachel Reddick, Matthew Cahill-Rowley, Doug Applegate, Mike Kozina, Warit Mitthumsiri, Chihway Chang, 
Max Swiatlowski, Sonya Mollinger, Alexis Charles, and Crystal Bray.  
I know I am missing others but you have all been wonderful companions
over the last several years and I thank you for being in my life. 

I thank Song Wang in particular for being my best buddy.  Thank you for the
many talks over lunch and the many tennis lessons. 
I thank Kurt Barry for being my best gym buddy.

I would like to recognize my adviser Roger Romani for 
feedback on my projects and resources.
For additional feedback on my thesis, I thank Hongjun An.
I would like to acknowledge Peter Michelson and 
the Vice Provost of Graduate Education for my funding.
I would like to thank my committee for their time and 
expertise:
Roger Blandford, Phil Bucksbaum, Stephen Cooper, and Vahe Petrosian.

For my data (and interest in my work) I thank
Dick Manchester, Simon Johnston, Matthew Kerr, Peter den Hartog, and Tyrel Johnson.

A very special thank you to my office mates
Michael Shaw and Adam van Etten for keeping me entertained and
delighted everyday.  I acknowledge Kyle Watters for helping
me get started on my project in the very beginning.

For keeping the computers up and running I am grateful to
Glenn Morris, 
Stuart Marshall, and
SLAC Computing.

For all sorts of other support I thank
David Stricker,
Christine Aguilar,
Ziba Mahdavi, Martha Siegel, Anika Green, and Chris Golde.


Finally, I thank my family for everything else.  I thank 
my mom for always being there when I needed to talk and my
sister for being my best friend.  
I thank my partner Joshua Lande for 
his love and support and for the many adventures we have gone on together, big and small.  
